\begin{thebibliography}{99}
\bibitem{hochstein2023toward} Hochstein, Rachel E and Harmeling, Colleen M and Perko, Taylor. {T}oward a theory of consumer digital trust: meta-analytic evidence of its role in the effectiveness of user-generated content. \textit{Journal of the Academy of Marketing Science}, 1--21, 2023. Springer.

\bibitem{krizhevsky2012imagenet} Krizhevsky, Alex and Sutskever, Ilya and Hinton, Geoffrey E. {I}magenet classification with deep convolutional neural networks. \textit{Advances in neural information processing systems}, 25, 2012.

\bibitem{cui2015global} Cui, Qing and Bai, Feng-Shan and Gao, Bin and Liu, Tie-Yan. {G}lobal optimization for advertisement selection in sponsored search. \textit{Journal of Computer Science and Technology}, 30, 295--310, 2015. Springer.

\bibitem{barajas2022online} Barajas, Joel and Bhamidipati, Narayan and Shanahan, James G. {O}nline advertising incrementality testing: {P}ractical lessons, paid search and {E}merging challenges. In \textit{European Conference on Information Retrieval}, pp. 575--581. Springer, 2022.

\bibitem{kant2021history} Kant, Tanya. {A} History of the {D}ata-{T}racked {U}ser. \textit{The MIT Press Reader}, 2021. \url{https://thereader.mitpress.mit.edu/a-history-of-the-data-tracked-user/}.

\bibitem{ellam2003overture} Ellam, Andrew and Ottaviani, Marco. {O}verture and {G}oogle: {I}nternet {P}ay-{P}er-{C}lick ({P}PC) {A}dvertising {A}uctions. \textit{London Business School Case Study CS-03-022}, 2003.

\bibitem{wsj2003yahoooverture} Wall Street Journal Staff. {Y}ahoo {A}grees to {A}cquire {O}verture {F}or \textbackslash \textdollar 1.63 {B}illion. \textit{The Wall Street Journal}, 2003. \url{https://www.wsj.com/articles/SB105818965623153600}.

\bibitem{wikipedia-cpm} Wikipedia contributors. {C}ost per mille --- {W}ikipedia, {T}he {F}ree {E}ncyclopedia. [Online; accessed 23-January-2025], 2025. \url{https://en.wikipedia.org/wiki/Cost\_per\_mille}.

\bibitem{hohnhold2015focusing} Hohnhold, Henning and O\textquotesingle Brien, Deirdre and Tang, Diane. {F}ocusing on the long-term: {I}t\textquotesingle s good for users and business. In \textit{Proceedings of the 21th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, pp. 1849--1858, 2015.

\bibitem{hu2004performance} Hu, Yu Jeffrey. {P}erformance-based pricing models in online advertising. \textit{Available at SSRN 501082}, 2004.

\bibitem{dimitrakakis2018decision} Dimitrakakis, Christos and Ortner, Ronald. {D}ecision making under uncertainty and reinforcement learning. \textit{Book available at http://www. cse. chalmers. se}, 2018. Springer.

\bibitem{koutsopoulos2016native} Koutsopoulos, Iordanis and Spentzouris, Panagiotis. {N}ative advertisement selection and allocation in social media post feeds. In \textit{Machine Learning and Knowledge Discovery in Databases: European Conference, ECML PKDD 2016, Riva del Garda, Italy, September 19-23, 2016, Proceedings, Part I 16}, pp. 588--603. Springer, 2016.

\bibitem{yan2020ads} Yan, Jinyun and Xu, Zhiyuan and Tiwana, Birjodh and Chatterjee, Shaunak. {A}ds allocation in feed via constrained optimization. In \textit{Proceedings of the 26th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining}, pp. 3386--3394, 2020.

\bibitem{russo2018tutorial} Russo, Daniel J and Van Roy, Benjamin and Kazerouni, Abbas and Osband, Ian and Wen, Zheng and others. {A} Tutorial on {T}hompson {S}ampling. \textit{Foundations and Trends\textregistered  in Machine Learning}, 11, 1--96, 2018. Now Publishers, Inc.

\bibitem{foster2020beyond} Foster, Dylan and Rakhlin, Alexander. {B}eyond ucb: {O}ptimal and efficient contextual bandits with regression oracles. In \textit{International Conference on Machine Learning}, pp. 3199--3210. PMLR, 2020.

\bibitem{fain2006sponsored} Fain, Daniel C and Pedersen, Jan O. {S}ponsored search: {A} brief history. \textit{Bulletin-American Society For Information Science And Technology}, 32, 12, 2006.

\bibitem{yi2014beyond} Yi, Xing and Hong, Liangjie and Zhong, Erheng and Liu, Nanthan Nan and Rajan, Suju. {B}eyond clicks: dwell time for personalization. In \textit{Proceedings of the 8th ACM Conference on Recommender systems}, pp. 113--120, 2014.

\bibitem{chakrabarti2008contextual} Chakrabarti, Deepayan and Agarwal, Deepak and Josifovski, Vanja. {C}ontextual advertising by combining relevance with click feedback. In \textit{Proceedings of the 17th international conference on World Wide Web}, pp. 417--426, 2008.

\bibitem{linden2003amazon} Linden, Greg and Smith, Brent and York, Jeremy. {A}mazon. com recommendations: {I}tem-to-item collaborative filtering. \textit{IEEE Internet computing}, 7, 76--80, 2003. IEEE.

\bibitem{abrams2007personalized} Abrams, Zo{\"e} and Vee, Erik. {P}ersonalized ad delivery when ads fatigue: {A}n approximation algorithm. In \textit{International Workshop on Web and Internet Economics}, pp. 535--540. Springer, 2007.

\bibitem{bietti2021contextual} Bietti, Alberto and Agarwal, Alekh and Langford, John. {A} contextual bandit bake-off. \textit{Journal of Machine Learning Research}, 22, 1--49, 2021.

\bibitem{baltescu2022itemsage} Baltescu, Paul and Chen, Haoyu and Pancha, Nikil and Zhai, Andrew and Leskovec, Jure and Rosenberg, Charles. {I}temsage: {L}earning product embeddings for shopping recommendations at pinterest. In \textit{Proceedings of the 28th ACM SIGKDD Conference on Knowledge Discovery and Data Mining}, pp. 2703--2711, 2022.

\bibitem{xia2023transact} Xia, Xue and Eksombatchai, Pong and Pancha, Nikil and Badani, Dhruvil Deven and Wang, Po-Wei and Gu, Neng and Joshi, Saurabh Vishwas and Farahpour, Nazanin and Zhang, Zhiyuan and Zhai, Andrew. {T}ransact: {T}ransformer-based realtime user action model for recommendation at pinterest. In \textit{Proceedings of the 29th ACM SIGKDD Conference on Knowledge Discovery and Data Mining}, pp. 5249--5259, 2023.

\bibitem{google_adwords_blog_2005} Google AdWords Team. {O}fficial {G}oogle {A}dWords {B}log. Accessed: 2024-12-03, 2005. \url{https://adwords.googleblog.com/2005/}.

\bibitem{pancha2022pinnerformer} Pancha, Nikil and Zhai, Andrew and Leskovec, Jure and Rosenberg, Charles. {P}innerformer: {S}equence modeling for user representation at pinterest. In \textit{Proceedings of the 28th ACM SIGKDD conference on knowledge discovery and data mining}, pp. 3702--3712, 2022.

\bibitem{he2018nais} He, Xiangnan and He, Zhankui and Song, Jingkuan and Liu, Zhenguang and Jiang, Yu-Gang and Chua, Tat-Seng. N{A}IS: {N}eural attentive item similarity model for recommendation. \textit{IEEE Transactions on Knowledge and Data Engineering}, 30, 2354--2366, 2018. IEEE.

\bibitem{Bengio1994} Bengio, Yoshua and Simard, Patrice and Frasconi, Paolo. {L}earning {L}ong-{T}erm {D}ependencies with {G}radient {D}escent is {D}ifficult. \textit{IEEE Transactions on Neural Networks}, 5, 157--166, 1994. IEEE. \url{https://www.cs.toronto.edu/\textasciitilde hinton/absps/bengio+al94.pdf}.

\bibitem{kang2018sasrec} Kang, Wang-Cheng and McAuley, Julian. {S}elf-{A}ttentive {S}equential {R}ecommendation. In \textit{Proceedings of the 2018 IEEE International Conference on Data Mining (ICDM)}, pp. 197--206, 2018. \url{https://arxiv.org/pdf/1808.09781}.

\bibitem{Sutskever2014} Sutskever, Ilya and Vinyals, Oriol and Le, Quoc V. {S}equence to sequence learning with neural networks. In \textit{Advances in Neural Information Processing Systems (NeurIPS)}, pp. 3104--3112, 2014. \url{https://papers.nips.cc/paper\_files/paper/2014/file/a14ac55a4f27472c5d894ec1c3c743d2-Paper.pdf}.

\bibitem{agarwal2020optimistic} Agarwal, Rishabh and Schuurmans, Dale and Norouzi, Mohammad. {A}n {O}ptimistic {P}erspective on {O}ffline {R}einforcement {L}earning. In \textit{International Conference on Machine Learning (ICML)}, pp. 104\textendash 114, 2020.

\bibitem{Schein2002} Schein, Andrew I. and Popescul, Alexandrin and Ungar, Lyle H. and Pennock, David M.. {M}ethods and {M}etrics for {C}old-start {R}ecommendations. In \textit{Proceedings of the 25th annual international ACM SIGIR conference on Research and development in information retrieval (SIGIR \textquotesingle 02)}, pp. 253--260, 2002.

\bibitem{Bobadilla2013} Bobadilla, Jesus and Ortega, Fernando and Hernando, Antonio and Guti\textbackslash {\'e}rrez, Arturo. {R}ecommender systems survey. \textit{Knowledge-Based Systems}, 46, 109--132, 2013.

\bibitem{Pascanu2013} Pascanu, Razvan and Mikolov, Tomas and Bengio, Yoshua. {O}n the difficulty of training recurrent neural networks. In \textit{Proceedings of the 30th International Conference on Machine Learning (ICML)}, pp. 1310--1318, 2013. PMLR. \url{http://proceedings.mlr.press/v28/pascanu13.pdf}.

\bibitem{gao2024mamba} Gao, Anningzhe and Dai, Shan and Hu, Yan. {M}amba hawkes process. \textit{arXiv preprint arXiv:2407.05302}, 2024.

\bibitem{vaswani2017attention} Vaswani, A. {A}ttention is all you need. \textit{Advances in Neural Information Processing Systems}, 2017.

\bibitem{Mehrotra2020} Rishabh Mehrotra and Niannan Xue and Mounia Lalmas. {B}andit {B}ased {O}ptimization of {M}ultiple {O}bjectives on a {M}usic 
{S}treaming {P}latform. In \textit{Proceedings of the 26th ACM SIGKDD International Conference on 
Knowledge Discovery \& Data Mining (KDD \textquotesingle 20)}, pp. 3224--3233, 2020.

\bibitem{Jannach2023} Dietmar Jannach and Himan Abdollahpouri. {A} Survey on {M}ulti-{O}bjective {R}ecommender {S}ystems. \textit{Frontiers in Big Data}, 6, 2023.

\bibitem{Mehrotra2018} Rishabh Mehrotra and James McInerney and Hugues Bouchard and  Mounia Lalmas and Fernando Diaz. {T}owards a {F}air {M}arketplace: {C}ounterfactual {E}valuation of the 
{T}rade-off between {R}elevance, {F}airness \& {S}atisfaction in 
{R}ecommendation {S}ystems. In \textit{Proceedings of the 27th ACM International Conference on Information 
and Knowledge Management (CIKM \textquotesingle 18)}, 2018.

\bibitem{Zhou2019} Guorui Zhou and Na Mou and Ying Fan and Qi Pi and Weijie Bian and  Chang Zhou and Xiaoqiang Zhu and Kun Gai. {D}eep {I}nterest {E}volution {N}etwork for {C}lick-{T}hrough {R}ate {P}rediction. In \textit{Proceedings of the 33rd AAAI Conference on Artificial Intelligence (AAAI)}, pp. 5941--5948, 2019.

\bibitem{Michel2019} Michel, Paul and Levy, Omer and Neubig, Graham. {A}re {S}ixteen {H}eads {R}eally {B}etter {T}han {O}ne?. In \textit{Advances in Neural Information Processing Systems 32 (NeurIPS)}, pp. 14014--14024, 2019.

\bibitem{Voita2019} Elena Voita and David Talbot and Fedor Moiseev and Rico Sennrich and  Ivan Titov. {A}nalyzing {M}ulti-{H}ead {S}elf-{A}ttention: {S}pecialized {H}eads {D}o the 
{H}eavy {L}ifting, the {R}est {C}an {B}e {P}runed. In \textit{Proceedings of the 57th Annual Meeting of the Association for 
Computational Linguistics (ACL)}, pp. 5797--5808, 2019.

\bibitem{Kang2018} Wang-Cheng Kang and Julian McAuley. {S}elf-{A}ttentive {S}equential {R}ecommendation. In \textit{2018 IEEE International Conference on Data Mining (ICDM)}, pp. 197--206, 2018.

\bibitem{chen2022off} Chen, Minmin and Xu, Can and Gatto, Vince and Jain, Devanshu and Kumar, Aviral and Chi, Ed. {O}ff-policy actor-critic for recommender systems. In \textit{Proceedings of the 16th ACM Conference on Recommender Systems}, pp. 338--349, 2022.

\bibitem{amodei2016concrete} Amodei, Dario and Olah, Chris and Steinhardt, Jacob and Christiano, Paul and Schulman, John and Man{\'e}, Dan. {C}oncrete problems in {A}I safety. \textit{arXiv preprint arXiv:1606.06565}, 2016.

\bibitem{carrion2021blending} Carrion, Carlos and Wang, Zenan and Nair, Harikesh and Luo, Xianghong and Lei, Yulin and Lin, Xiliang and Chen, Wenlong and Hu, Qiyu and Peng, Changping and Bao, Yongjun and others. {B}lending advertising with organic content in e-commerce: {A} virtual bids optimization approach. \textit{arXiv preprint arXiv:2105.13556}, 2021.

\bibitem{zhang2018whole} Zhang, Weiru and Wei, Chao and Meng, Xiaonan and Hu, Yi and Wang, Hao. {T}he whole-page optimization via dynamic ad allocation. In \textit{Companion Proceedings of the The Web Conference 2018}, pp. 1407--1411, 2018.

\bibitem{sagtani2024ad} Sagtani, Hitesh and Jhawar, Madan Gopal and Mehrotra, Rishabh and Jeunen, Olivier. {A}d-load {B}alancing via {O}ff-policy {L}earning in a {C}ontent {M}arketplace. In \textit{Proceedings of the 17th ACM International Conference on Web Search and Data Mining}, pp. 586--595, 2024.

\bibitem{van2016deep} Van Hasselt, Hado and Guez, Arthur and Silver, David. {D}eep reinforcement learning with double q-learning. In \textit{Proceedings of the AAAI conference on artificial intelligence}, 2016.

\bibitem{shahriari2015taking} Shahriari, Bobak and Swersky, Kevin and Wang, Ziyu and Adams, Ryan P and De Freitas, Nando. {T}aking the human out of the loop: {A} review of {B}ayesian optimization. \textit{Proceedings of the IEEE}, 104, 148--175, 2015. IEEE.

\bibitem{schulman2017proximal} Schulman, John and Wolski, Filip and Dhariwal, Prafulla and Radford, Alec and Klimov, Oleg. {P}roximal policy optimization algorithms. \textit{arXiv preprint arXiv:1707.06347}, 2017.

\bibitem{mnih2016asynchronous} Mnih, Volodymyr and Badia, Adria Puigdomenech and Mirza, Mehdi and Graves, Alex and Lillicrap, Timothy and Harley, Tim and Silver, David and Kavukcuoglu, Koray. {A}synchronous methods for deep reinforcement learning. In \textit{International conference on machine learning}, pp. 1928--1937. PMLR, 2016.

\bibitem{auer2002finite} Auer, Peter and Cesa-Bianchi, Nicolo and Fischer, Paul. {F}inite-{T}ime {A}nalysis of the {M}ultiarmed {B}andit {P}roblem. \textit{Machine learning}, 47, 235--256, 2002. Springer.

\bibitem{swaminathan2015counterfactual} Swaminathan, Adith and Joachims, Thorsten. {C}ounterfactual risk minimization: {L}earning from logged bandit feedback. In \textit{International conference on machine learning}, pp. 814--823. PMLR, 2015.

\bibitem{levine2020offline} Levine, Sergey and Kumar, Aviral and Tucker, George and Fu, Justin. {O}ffline reinforcement learning: {T}utorial, review, and perspectives on open problems. \textit{arXiv preprint arXiv:2005.01643}, 2020.

\bibitem{agarwal2014taming} Agarwal, Alekh and Hsu, Daniel and Kale, Satyen and Langford, John and Li, Lihong and Schapire, Robert. {T}aming the monster: {A} fast and simple algorithm for contextual bandits. In \textit{International conference on machine learning}, pp. 1638--1646. PMLR, 2014.

\bibitem{dudik2011doubly} Dud{\i}́k, Miroslav and Langford, John and Li, Lihong. {D}oubly robust policy evaluation and learning. \textit{arXiv preprint arXiv:1103.4601}, 2011.

\bibitem{chapelle2011empirical} Chapelle, Olivier and Li, Lihong. {A}n empirical evaluation of thompson sampling. \textit{Advances in neural information processing systems}, 24, 2011.

\bibitem{galashov2019meta} Galashov, Alexandre and Schwarz, Jonathan and Kim, Hyunjik and Garnelo, Marta and Saxton, David and Kohli, Pushmeet and Eslami, SM and Teh, Yee Whye. {M}eta-learning surrogate models for sequential decision making. \textit{arXiv preprint arXiv:1903.11907}, 2019.

\bibitem{agarwal2016statistical} Agarwal, Deepak K and Chen, Bee-Chung. {S}tatistical methods for recommender systems., 2016. Cambridge University Press.

\bibitem{chen2009large} Chen, Bee-Chung and Pavlov, Dmitry and Canny, John F and Rijckaert, Lodewijk. {L}arge-scale {B}ehavioral {T}argeting. In \textit{Proceedings of the 15th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining (KDD \textquotesingle 09)}, pp. 209--218, 2009.

\bibitem{agarwal2019online} Agarwal, Deepak and Cornell, David and Huang, Bin and Lee, Bee-Chung Chen and Tang, Ruoxi and Zhang, Le and Wolf, Avery and Shi, Yuchen and Wang, Ye and Guo, Yin and Garimella, Srijan Kumar and Korolko, Nikita and Muthukrishnan, Sandeep. {O}nline {P}arameter {S}election for {W}eb-based {S}ervices. In \textit{Proceedings of the 25th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining (KDD \textquotesingle 19)}, pp. 1645--1653, 2019.

\bibitem{sagtani2023quantifying} Sagtani, Hitesh and Jhawar, Madan Gopal and Gupta, Akshat and Mehrotra, Rishabh. {Q}uantifying and leveraging user fatigue for interventions in recommender systems. In \textit{Proceedings of the 46th International ACM SIGIR Conference on Research and Development in Information Retrieval}, pp. 2293--2297, 2023.

\bibitem{mazoure2021improving} Mazoure, Bogdan and Mineiro, Paul and Srinath, Pavithra and Sedeh, Reza Sharifi and Precup, Doina and Swaminathan, Adith. {I}mproving long-term metrics in recommendation systems using short-horizon reinforcement learning. \textit{arXiv preprint arXiv:2106.00589}, 2021.

\bibitem{everitt2021reward} Everitt, Tom and Hutter, Marcus and Kumar, Ramana and Krakovna, Victoria. {R}eward tampering problems and solutions in reinforcement learning: {A} causal influence diagram perspective. \textit{Synthese}, 198, 6435--6467, 2021. Springer.

\bibitem{zhu2021overview} Zhu, Jie and Wu, Fengge and Zhao, Junsuo. {A}n overview of the action space for deep reinforcement learning. In \textit{Proceedings of the 2021 4th International Conference on Algorithms, Computing and Artificial Intelligence}, pp. 1--10, 2021.

\bibitem{nvidia_recommender_systems_2021} Carol McDonald. {H}ow to {B}uild a {D}eep {L}earning {P}owered {R}ecommender {S}ystem, {P}art 2. Accessed: 2024-11-19, 2021. \url{https://developer.nvidia.com/blog/how-to-build-a-winning-recommendation-system-part-2-deep-learning-for-recommender-systems/}.

\bibitem{lu2016partially} Lu, Zhongqi and Yang, Qiang. {P}artially observable {M}arkov decision process for recommender systems. \textit{arXiv preprint arXiv:1608.07793}, 2016.

\bibitem{kaelbling1998planning} Kaelbling, Leslie Pack and Littman, Michael L and Cassandra, Anthony R. {P}lanning and acting in partially observable stochastic domains. \textit{Artificial intelligence}, 101, 99--134, 1998. Elsevier.

\bibitem{wu2021partially} Wu, Yaxiong and Macdonald, Craig and Ounis, Iadh. {P}artially observable reinforcement learning for dialog-based interactive recommendation. In \textit{Proceedings of the 15th ACM conference on recommender systems}, pp. 241--251, 2021.

\bibitem{silberstein2023combating} Silberstein, Natalia and Shoham, Or and Klein, Assaf. {C}ombating {A}d {F}atigue via {F}requency-{R}ecency {F}eatures in {O}nline {A}dvertising {S}ystems. In \textit{Proceedings of the 32nd ACM International Conference on Information and Knowledge Management}, pp. 4822--4828, 2023.

\bibitem{zheng2024cadrl} Zheng, Shangfei and Yin, Hongzhi and Chen, Tong and Kong, Xiangjie and Hou, Jian and Zhao, Pengpeng. C{A}DR{L}: {C}ategory-aware {D}ual-agent {R}einforcement {L}earning for {E}xplainable {R}ecommendations over {K}nowledge {G}raphs. \textit{arXiv preprint arXiv:2408.03166}, 2024.

\bibitem{chen2021user} Chen, Minmin and Chang, Bo and Xu, Can and Chi, Ed H. {U}ser response models to improve a reinforce recommender system. In \textit{Proceedings of the 14th ACM international conference on web search and data mining}, pp. 121--129, 2021.

\bibitem{wang2022surrogate} Wang, Yuyan and Sharma, Mohit and Xu, Can and Badam, Sriraj and Sun, Qian and Richardson, Lee and Chung, Lisa and Chi, Ed H and Chen, Minmin. {S}urrogate for long-term user experience in recommender systems. In \textit{Proceedings of the 28th ACM SIGKDD conference on knowledge discovery and data mining}, pp. 4100--4109, 2022.

\bibitem{zhao2021dear} Zhao, Xiangyu and Gu, Changsheng and Zhang, Haoshenglun and Yang, Xiwang and Liu, Xiaobing and Tang, Jiliang and Liu, Hui. {D}ear: {D}eep reinforcement learning for online advertising impression in recommender systems. In \textit{Proceedings of the AAAI conference on artificial intelligence}, pp. 750--758, 2021.

\bibitem{shim2022comparison} Shim, Kyuhong and Sung, Wonyong. {A} Comparison of {T}ransformer, {C}onvolutional, and {R}ecurrent {N}eural {N}etworks on {P}honeme {R}ecognition. \textit{arXiv preprint arXiv:2210.00367}, 2022. \url{https://arxiv.org/abs/2210.00367}.

\bibitem{ma2018modeling} Ma, Jiaqi and Zhao, Zhe and Yi, Xinyang and Chen, Jilin and Hong, Lichan and Chi, Ed H. {M}odeling task relationships in multi-task learning with multi-gate mixture-of-experts. In \textit{Proceedings of the 24th ACM SIGKDD international conference on knowledge discovery \& data mining}, pp. 1930--1939, 2018.

\bibitem{an2024tmh} An, Zijian and Joe, Inwhee. T{M}H: {T}wo-{T}ower {M}ulti-{H}ead {A}ttention neural network for {C}TR prediction. \textit{Plos one}, 19, e0295440, 2024. Public Library of Science San Francisco, CA USA.

\bibitem{lyu2023entire} Lyu, Shanshan and Chen, Qiwei and Zhuang, Tao and Ge, Junfeng. {E}ntire {S}pace {L}earning {F}ramework: {U}nbias {C}onversion {R}ate {P}rediction in {F}ull {S}tages of {R}ecommender {S}ystem. \textit{arXiv preprint arXiv:2303.00276}, 2023.

\bibitem{zhao2019recommending} Zhao, Zhe and Hong, Lichan and Wei, Li and Chen, Jilin and Nath, Aniruddh and Andrews, Shawn and Kumthekar, Aditee and Sathiamoorthy, Maheswaran and Yi, Xinyang and Chi, Ed. {R}ecommending what video to watch next: a multitask ranking system. In \textit{Proceedings of the 13th ACM conference on recommender systems}, pp. 43--51, 2019.

\bibitem{zou2019reinforcement} Zou, Lixin and Xia, Long and Ding, Zhuoye and Song, Jiaxing and Liu, Weidong and Yin, Dawei. {R}einforcement learning to optimize long-term user engagement in recommender systems. In \textit{Proceedings of the 25th ACM SIGKDD international conference on knowledge discovery \& data mining}, pp. 2810--2818, 2019.

\bibitem{Theocharous-2015} Theocharous, Georgios and Thomas, Philip S. and Ghavamzadeh, Mohammad. {P}ersonalized ad recommendation for life-time value optimization. In \textit{Proceedings of the 24th International Joint Conference on Artificial Intelligence (IJCAI)}, pp. 1807--1813, 2015.

\bibitem{mcdonald2023spotify} McDonald, Thomas M. and Maystre, Lucas and Lalmas, Mounia and Russo, Daniel and Ciosek, Kamil. {O}ptimizing for the {L}ong-{T}erm {W}ithout {D}elay., 2023. \url{https://research.atspotify.com/2023/07/optimizing-for-the-long-term-without-delay/}.

\bibitem{kaelbling1996reinforcement} Kaelbling, Leslie Pack and Littman, Michael L and Moore, Andrew W. {R}einforcement learning: {A} survey. \textit{Journal of artificial intelligence research}, 4, 237--285, 1996.

\bibitem{FrozenLakeGymnasium2023} . {F}rozen {L}ake {T}utorial. Accessed: 2023-03-05, 2023.

\bibitem{dulac2019challenges} Dulac-Arnold, Gabriel and Mankowitz, Daniel and Hester, Todd. {C}hallenges of real-world reinforcement learning. \textit{arXiv preprint arXiv:1904.12901}, 2019.

\bibitem{kaplan2020scaling} Kaplan, Jared and McCandlish, Sam and Henighan, Tom and Brown, Tom B and Chess, Benjamin and Child, Rewon and Gray, Scott and Radford, Alec and Wu, Jeffrey and Amodei, Dario. {S}caling laws for neural language models. \textit{arXiv preprint arXiv:2001.08361}, 2020.

\bibitem{brown2020language} Brown, Tom and Mann, Benjamin and Ryder, Nick and Subbiah, Melanie and Kaplan, Jared D and Dhariwal, Prafulla and Neelakantan, Arvind and Shyam, Pranav and Sastry, Girish and Askell, Amanda and others. {L}anguage models are few-shot learners. \textit{Advances in neural information processing systems}, 33, 1877--1901, 2020.

\bibitem{russell2016artificial} Russell, Stuart J and Norvig, Peter. {A}rtificial intelligence: a modern approach., 2016. pearson.

\bibitem{puterman2014markov} Puterman, Martin L. {M}arkov decision processes: discrete stochastic dynamic programming., 2014. John Wiley \& Sons.

\bibitem{montague1999reinforcement} Montague, P Read. {R}einforcement learning: an introduction, by {S}utton, {R}S and {B}arto, {A}G. \textit{Trends in cognitive sciences}, 3, 360, 1999. Elsevier.

\bibitem{afsar2022reinforcement} Afsar, M Mehdi and Crump, Trafford and Far, Behrouz. {R}einforcement learning based recommender systems: {A} survey. \textit{ACM Computing Surveys}, 55, 1--38, 2022. ACM New York, NY.

\bibitem{zhou2016latent} Zhou, Li and Brunskill, Emma. {L}atent contextual bandits and their application to personalized recommendations for new users. \textit{arXiv preprint arXiv:1604.06743}, 2016.

\bibitem{sharma2017learning} Sharma, Sahil and Suresh, Aravind and Ramesh, Rahul and Ravindran, Balaraman. {L}earning to factor policies and action-value functions: {F}actored action space representations for deep reinforcement learning. \textit{arXiv preprint arXiv:1705.07269}, 2017.

\bibitem{glanois2024survey} Glanois, Claire and Weng, Paul and Zimmer, Matthieu and Li, Dong and Yang, Tianpei and Hao, Jianye and Liu, Wulong. {A} survey on interpretable reinforcement learning. \textit{Machine Learning}, 1--44, 2024. Springer.

\bibitem{puiutta2020explainable} Puiutta, Erika and Veith, Eric MSP. {E}xplainable reinforcement learning: {A} survey. In \textit{International cross-domain conference for machine learning and knowledge extraction}, pp. 77--95. Springer, 2020.

\bibitem{tavakoli2018action} Tavakoli, Arash and Pardo, Fabio and Kormushev, Petar. {A}ction branching architectures for deep reinforcement learning. In \textit{Proceedings of the aaai conference on artificial intelligence}, 2018.

\bibitem{liu2025reducing} Liu, Wenzhang and Jin, Lianjun and Ren, Lu and Mu, Chaoxu and Sun, Changyin. {R}educing {A}ction {S}pace for {D}eep {R}einforcement {L}earning via {C}ausal {E}ffect {E}stimation. \textit{arXiv preprint arXiv:2501.14543}, 2025.

\bibitem{zhu2024discretizing} Zhu, Yuanyang and Wang, Zhi and Zhu, Yuanheng and Chen, Chunlin and Zhao, Dongbin. {D}iscretizing {C}ontinuous {A}ction {S}pace {W}ith {U}nimodal {P}robability {D}istributions for {O}n-{P}olicy {R}einforcement {L}earning. \textit{IEEE Transactions on Neural Networks and Learning Systems}, 2024. IEEE.

\bibitem{frozenlake} Gym Documentation Team. {F}rozen {L}ake {E}nvironment in {O}pen{A}I {G}ym. Accessed: 23 August 2024, 2024.

\bibitem{brockman2016openai} Brockman, Greg and Cheung, Vicki and Pettersson, Ludwig and Schneider, Jonas and Schulman, John and Tang, Jie and Zaremba, Wojciech. {O}pen{A}I {G}ym. \textit{arXiv preprint arXiv:1606.01540}, 2016. \url{https://arxiv.org/abs/1606.01540}.

\bibitem{danescu2010competing} Danescu-Niculescu-Mizil, Cristian and Broder, Andrei Z and Gabrilovich, Evgeniy and Josifovski, Vanja and Pang, Bo. {C}ompeting for users\textquotesingle  attention: on the interplay between organic and sponsored search results. In \textit{Proceedings of the 19th international conference on World wide web}, pp. 291--300, 2010.

\bibitem{dulac2021challenges} Dulac-Arnold, Gabriel and Levine, Nir and Mankowitz, Daniel J and Li, Jerry and Paduraru, Cosmin and Gowal, Sven and Hester, Todd. {C}hallenges of real-world reinforcement learning: definitions, benchmarks and analysis. \textit{Machine Learning}, 110, 2419--2468, 2021. Springer.

\bibitem{vonNeumannMorgenstern1944} John von Neumann and Oskar Morgenstern. {T}heory of {G}ames and {E}conomic {B}ehavior., 1944. Princeton University Press.

\bibitem{schwartz2017customer} Schwartz, Eric M and Bradlow, Eric T and Fader, Peter S. {C}ustomer acquisition via display advertising using multi-armed bandit experiments. \textit{Marketing Science}, 36, 500--522, 2017. INFORMS.

\bibitem{engel2008incorporating} Engel, Yagil and Chickering, David Maxwell. {I}ncorporating user utility into sponsored-search auctions. In \textit{Proceedings of the 7th international joint conference on Autonomous agents and multiagent systems-Volume 3}, pp. 1565--1568, 2008.

\bibitem{Stigler1950} George J. Stigler. {T}he {D}evelopment of {U}tility {T}heory. {I}. \textit{Journal of Political Economy}, 58, 307--327, 1950. University of Chicago Press.

\bibitem{wen2019learning} Wen, Ying and Mu, Yao and Ester, Martin. {L}earning {M}ulti-{O}bjective {R}ewards and {U}ser {U}tility {F}unction in {R}ecommender {S}ystems. In \textit{Proceedings of the 28th International Joint Conference on Artificial Intelligence (IJCAI)}, pp. 3719--3725. International Joint Conferences on Artificial Intelligence Organization, 2019. \url{https://www.ijcai.org/proceedings/2019/0532.pdf}.

\bibitem{kuleshov2014algorithms} Kuleshov, Volodymyr and Precup, Doina. {A}lgorithms for {M}ulti-{A}rmed {B}andit {P}roblems. \textit{arXiv preprint arXiv:1402.6028}, 2014. \url{https://arxiv.org/abs/1402.6028}.

\bibitem{thompson1933likelihood} Thompson, William R.. {O}n the likelihood that one unknown probability exceeds another in view of the evidence of two samples. \textit{Biometrika}, 25, 285--294, 1933. Oxford University Press.

\bibitem{villar2015multi} Villar, Sof{\i}́a S. and Bowden, Jack and Wason, James. {M}ulti-armed {B}andit {M}odels for the {O}ptimal {D}esign of {C}linical {T}rials: {B}enefits and {C}hallenges. \textit{Statistical Science}, 30, 199--215, 2015. Institute of Mathematical Statistics. \url{https://projecteuclid.org/euclid.ss/1432829203}.

\bibitem{burtini2015improving} Burtini, Giuseppe and Loeppky, Jason L. and Lawrence, Ramon. {I}mproving {O}nline {M}arketing {E}xperiments with {D}rifting {M}ulti-armed {B}andits. In \textit{Proceedings of the 7th International Conference on Agents and Artificial Intelligence (ICAART)}, pp. 135--146. SCITEPRESS, 2015.

\bibitem{robbins1952sequential} Herbert Robbins. {S}ome aspects of the sequential design of experiments. \textit{Bulletin of the American Mathematical Society}, 58, 527--535, 1952. \url{https://projecteuclid.org/euclid.bams/1183517370}.

\bibitem{ccelik2023ad} {\c C}elik, Fatih and {\c C}am, Mehmet Safa and Koseoglu, Mehmet Ali. {A}d avoidance in the digital context: {A} systematic literature review and research agenda. \textit{International Journal of Consumer Studies}, 47, 2071--2105, 2023. Wiley Online Library.

\bibitem{vorotilov2023scaling} Vorotilov, Vladislav and Shugaepov, Ilnur. {S}caling the {I}nstagram {E}xplore {R}ecommendations {S}ystem. \textit{Engineering at Meta}, 2023. \url{https://engineering.fb.com/2023/08/09/ml-applications/scaling-instagram-explore-recommendations-system/}.

\bibitem{zhao2024survey} Zhao, Yu and Liu, Fang. {A} survey of retrieval algorithms in ad and content recommendation systems. \textit{arXiv preprint arXiv:2407.01712}, 2024.

\bibitem{xu2023optimizing} Xu, Ruiyang and Bhandari, Jalaj and Korenkevych, Dmytro and Liu, Fan and He, Yuchen and Nikulkov, Alex and Zhu, Zheqing. {O}ptimizing long-term value for auction-based recommender systems via on-policy reinforcement learning. In \textit{Proceedings of the 17th ACM Conference on Recommender Systems}, pp. 955--962, 2023.

\bibitem{wu2018beyond} Wu, Siqi and Rizoiu, Marian-Andrei and Xie, Lexing. {B}eyond views: {M}easuring and predicting engagement in online videos. In \textit{Proceedings of the International AAAI Conference on Web and Social Media}, 2018.

\bibitem{wu2017returning} Wu, Qingyun and Wang, Hongning and Hong, Liangjie and Shi, Yue. {R}eturning is believing: {O}ptimizing long-term user engagement in recommender systems. In \textit{Proceedings of the 2017 ACM on Conference on Information and Knowledge Management}, pp. 1927--1936, 2017.

\bibitem{gauci2018horizon} Gauci, Jason and Conti, Edoardo and Liang, Yitao and Virochsiri, Kittipat and He, Yuchen and Kaden, Zachary and Narayanan, Vivek and Ye, Xiaohui and Chen, Zhengxing and Fujimoto, Scott. {H}orizon: {F}acebook\textquotesingle s open source applied reinforcement learning platform. \textit{arXiv preprint arXiv:1811.00260}, 2018.

\bibitem{yi2023progressive} Yi, Congrui and Zumwalt, David and Ni, Zijian and Chakrabarti, Shreya. {P}rogressive horizon learning: {A}daptive long term optimization for personalized recommendation. In \textit{Proceedings of the 17th ACM Conference on Recommender Systems}, pp. 940--946, 2023.

\bibitem{mcdonald2023impatient} McDonald, Thomas M and Maystre, Lucas and Lalmas, Mounia and Russo, Daniel and Ciosek, Kamil. {I}mpatient bandits: {O}ptimizing recommendations for the long-term without delay. In \textit{Proceedings of the 29th ACM SIGKDD Conference on Knowledge Discovery and Data Mining}, pp. 1687--1697, 2023.

\bibitem{lin2023survey} Lin, Yuanguo and Liu, Yong and Lin, Fan and Zou, Lixin and Wu, Pengcheng and Zeng, Wenhua and Chen, Huanhuan and Miao, Chunyan. {A} survey on reinforcement learning for recommender systems. \textit{IEEE Transactions on Neural Networks and Learning Systems}, 2023. IEEE.

\bibitem{van2024practical} van den Akker, Bram and Jeunen, Olivier and Li, Ying and London, Ben and Nazari, Zahra and Parekh, Devesh. {P}ractical {B}andits: {A}n {I}ndustry {P}erspective. In \textit{Proceedings of the 17th ACM International Conference on Web Search and Data Mining}, pp. 1132--1135, 2024.

\bibitem{li2010contextual} Li, Lihong and Chu, Wei and Langford, John and Schapire, Robert E. {A} contextual-bandit approach to personalized news article recommendation. In \textit{Proceedings of the 19th international conference on World wide web}, pp. 661--670, 2010.

\bibitem{bubeck2012regret} Bubeck, S{\'e}bastien and Cesa-Bianchi, Nicolo and others. {R}egret analysis of stochastic and nonstochastic multi-armed bandit problems. \textit{Foundations and Trends\textregistered  in Machine Learning}, 5, 1--122, 2012. Now Publishers, Inc.

\bibitem{lambert2023entangled} Lambert, Nathan and Gilbert, Thomas Krendl and Zick, Tom. {E}ntangled preferences: {T}he history and risks of reinforcement learning and human feedback. \textit{arXiv preprint arXiv:2310.13595}, 2023.

\bibitem{vouros2022explainable} Vouros, George A. {E}xplainable deep reinforcement learning: state of the art and challenges. \textit{ACM Computing Surveys}, 55, 1--39, 2022. ACM New York, NY.

\bibitem{ie2019slateq} Ie, Eugene and Jain, Vihan and Wang, Jing and Narvekar, Sanmit and Agarwal, Ritesh and Wu, Rui and Cheng, Heng-Tze and Chandra, Tushar and Boutilier, Craig. {S}late{Q}: {A} Tractable {D}ecomposition for {R}einforcement {L}earning with {R}ecommendation {S}ets.. In \textit{IJCAI}, pp. 2592--2599, 2019.

\bibitem{zhao2020jointly} Zhao, Xiangyu and Zheng, Xudong and Yang, Xiwang and Liu, Xiaobing and Tang, Jiliang. {J}ointly {L}earning to {R}ecommend and {A}dvertise. In \textit{Proceedings of the 26th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining}, pp. 3319--3327, 2020. ACM.

\bibitem{ie2019recsim} Ie, Eugene and Hsu, Chih-wei and Mladenov, Martin and Jain, Vihan and Narvekar, Sanmit and Wang, Jing and Wu, Rui and Boutilier, Craig. {R}ecsim: {A} configurable simulation platform for recommender systems. \textit{arXiv preprint arXiv:1909.04847}, 2019.

\bibitem{ie2019reinforcement} Ie, Eugene and Jain, Vihan and Wang, Jing and Narvekar, Sanmit and Agarwal, Ritesh and Wu, Rui and Cheng, Heng-Tze and Lustman, Morgane and Gatto, Vince and Covington, Paul and others. {R}einforcement learning for slate-based recommender systems: {A} tractable decomposition and practical methodology. \textit{arXiv preprint arXiv:1905.12767}, 2019.

\bibitem{mcmahan2013ad} McMahan, H Brendan and Holt, Gary and Sculley, David and Young, Michael and Ebner, Dietmar and Grady, Julian and Nie, Lan and Phillips, Todd and Davydov, Eugene and Golovin, Daniel and others. {A}d click prediction: a view from the trenches. In \textit{Proceedings of the 19th ACM SIGKDD international conference on Knowledge discovery and data mining}, pp. 1222--1230, 2013.

\bibitem{yan2009much} Yan, Jun and Liu, Ning and Wang, Gang and Zhang, Wen and Jiang, Yun and Chen, Zheng. {H}ow much can behavioral targeting help online advertising?. In \textit{Proceedings of the 18th international conference on World wide web}, pp. 261--270, 2009.

\bibitem{nielsen2017advertising} Nielsen. {W}hen {I}t {C}omes to {A}dvertising {E}ffectiveness, {W}hat {I}s {K}ey?. Accessed: 2025-03-27, 2017. \url{https://www.nielsen.com/insights/2017/when-it-comes-to-advertising-effectiveness-what-is-key/}.

\bibitem{zhao2018deep} Zhao, Jun and Qiu, Guang and Guan, Ziyu and Zhao, Wei and He, Xiaofei. {D}eep reinforcement learning for sponsored search real-time bidding. In \textit{Proceedings of the 24th ACM SIGKDD international conference on knowledge discovery \& data mining}, pp. 1021--1030, 2018.

\bibitem{saha2021advertiming} Saha, Koustuv and Liu, Yozen and Vincent, Nicholas and Chowdhury, Farhan Asif and Neves, Leonardo and Shah, Neil and Bos, Maarten W. {A}dvertiming matters: {E}xamining user ad consumption for effective ad allocations on social media. In \textit{Proceedings of the 2021 CHI Conference on Human Factors in Computing Systems}, pp. 1--18, 2021.

\bibitem{yuan2020unbiased} Yuan, Bowen and Liu, Yaxu and Hsia, Jui-Yang and Dong, Zhenhua and Lin, Chih-Jen. {U}nbiased {A}d click prediction for position-aware advertising systems. In \textit{Proceedings of the 14th ACM Conference on Recommender Systems}, pp. 368--377, 2020.

\bibitem{tettoni2024discoverability} Anne-Laure Tettoni and Simon Dumas Primbault. {D}iscoverability in a {D}igital {L}ibrary: {A} Study of \textasciigrave \textasciigrave {R}abbit {H}oles\textquotesingle \textquotesingle  within {G}allica\textquotesingle s corpus. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1-20, 2024.

\bibitem{barré2024latent} Jean Barr{\'e}. {L}atent structures in french fiction. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 21-36, 2024.

\bibitem{arnold2024automated} Taylor Arnold and Lauren Tilton. {A}utomated {I}mage {C}olor {M}apping for a {H}istoric {P}hotographic {C}ollection. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 37-47, 2024.

\bibitem{bambaci2024steps} Luigi Bambaci and George Kiraz and Christine Roughan and Matthieu Freyder and Daniel St{\"o}kl Ben Ezra. {S}teps {T}owards {M}ining {M}anuscript {I}mages for {U}ntranscribed {T}exts: {A} Case {S}tudy {F}rom the {S}yriac {C}ollection at the {V}atican {L}ibrary. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 48-64, 2024.

\bibitem{levenson2024textual} Matthias Gille Levenson and Lucence Ing and Jean-Baptiste Camps. {T}extual {T}ransmission without {B}orders: {M}ultiple {M}ultilingual {A}lignment and {S}temmatology of the \textasciigrave \textasciigrave {L}ancelot en prose\textquotesingle \textquotesingle  ({M}edieval {F}rench, {C}astilian, {I}talian). In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 65-92, 2024.

\bibitem{jacobsen2024admiration} Mia Jacobsen and Ross Deans Kristensen-McLachlan. {A}dmiration and {F}rustration: {A} Multidimensional {A}nalysis of {F}anfiction. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 93-112, 2024.

\bibitem{ströbel2024bringing} Phillip B. Str{\"o}bel and Zejie Guo and {\"U}lk{\"u} Karag{\"o}z and Eva Maria Willi and Felix K. Maier. {B}ringing {R}ome to {L}ife: {E}valuating {H}istorical {I}mage {G}eneration. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 113-126, 2024.

\bibitem{zapata2024transformation} Pepe Ballesteros Zapata and Nina Arnold and Vappu Lukander and Ludovica Schaerf and Dario Negueruela del Castillo. {T}ransformation of {C}omposition and {G}aze {I}nteraction in {N}oli {M}e {T}angere {D}epictions from 1300\textendash 1600. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 127-136, 2024.

\bibitem{moss2024modeling} Fabian C. Moss and Eita Nakamura. {M}odeling the {E}volution of {H}armony in {P}opular {M}usic from {D}ifferent {C}ultural {C}ontexts. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 137-152, 2024.

\bibitem{lassen2024literary} Ida Marie S. Lassen and Pascale Feldkamp Moreira and Yuri Bizzoni and Kristoffer Nielbo. {L}iterary {C}anonicity and {A}lgorithmic {F}airness: {T}he {E}ffect of {A}uthor {G}ender on {C}lassification {M}odels. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 153-171, 2024.

\bibitem{bizzoni2024global} Yuri Bizzoni and Pascale Feldkamp and Kristoffer Nielbo. {G}lobal {C}oherence, {L}ocal {U}ncertainty - {T}owards a {T}heoretical {F}ramework for {A}ssessing {L}iterary {Q}uality. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 172-185, 2024.

\bibitem{zhou2024once} Naitian Zhou and David Bamman. {O}nce {M}ore, {W}ith {F}eeling: {M}easuring {E}motion of {A}cting {P}erformances in {C}ontemporary {A}merican {F}ilm. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 186-199, 2024.

\bibitem{gorène2024enhancing} Chahan Vidal-Gor{\`e}ne and Cl{\'e}ment Salah and No{\"e}mie Lucas and Ali{\'e}nor Decours-Perez and Antoine Perrier. {E}nhancing {A}rabic {M}aghribi {H}andwritten {T}ext {R}ecognition with {R}AS{A}M 2: {A} Comprehensive {D}ataset and {B}enchmarking. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 200-216, 2024.

\bibitem{neugarten2024catching} Julia Neugarten and Tess Dejaeghere and Pranaydeep Singh and Amanda Robin Hemmons and Julie M. Birkholz. {C}atching {F}eelings: {A}spect-{B}ased {S}entiment {A}nalysis for {F}anfiction {C}omments about {G}reek {M}yth. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 217-231, 2024.

\bibitem{griebel2024locating} Sarah Griebel and Becca Cohen and Lucian Li and Jiayu Liu and Jaihyun Park and Jana Perkins and Ted Underwood. {L}ocating the {L}eading {E}dge of {C}ultural {C}hange. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 232-245, 2024.

\bibitem{gabay2024birth} Simon Gabay and Thibault Cl{\'e}rice. {T}he birth of {F}rench orthography. {A} computational analysis of {F}rench spelling systems in diachrony. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 246-264, 2024.

\bibitem{karsdorp2024beyond} Folgert Karsdorp and Mike Kestemont and Margo de Koster. {B}eyond the {R}egister: {D}emographic {M}odeling of {A}rrest {P}atterns in 1879-1880 {B}russels. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 265-281, 2024.

\bibitem{konle2024on} Leonard Konle and Merten Kr{\"o}ncke and Fotis Jannidis and Simone Winko. {O}n the {U}nity of {L}iterary {C}hange. {T}he {D}evelopment of {E}motions in {G}erman {P}oetry, {P}rose, and {D}rama between 1850 and 1920 as a {T}est {C}ase. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 282-300, 2024.

\bibitem{dunbar2024getting} Maria Bekker-Nielsen Dunbar and Manex Agirrezabal and T{\o}nnes Bekker-Nielsen. {G}etting to grippe with influenza: an investigation of why the disease is called that. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 301-312, 2024.

\bibitem{priestley2024treebanks} Joel Priestley and Anders N{\o}klestad and Kristin Hagen and Anu Laanemets and Dag Trygve Truslew Haug. {T}reebanks for the ordinary working grammarian. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 313-321, 2024.

\bibitem{yu2024across} Ze Yu and Federico Pianzola. {A}cross the {P}ages: {A} Comparative {S}tudy of {R}eader {R}esponse to {W}eb {N}ovels in {C}hinese and {E}nglish on {Q}idian and {W}eb{N}ovel. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 322-333, 2024.

\bibitem{rodilla2024addressing} Patricia Martin-Rodilla and Leticia Tobalina-Pulido. {A}ddressing {U}ncertainty according to the {A}nnotator\textquotesingle s {E}xpertise in {A}rchaeological {D}ata {C}ollections: an {A}pproach from {F}uzzy {L}ogic. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 334-352, 2024.

\bibitem{kaldeli2024combining} Eirini Kaldeli and Alexandros Chortaras and Vassilis Lyberatos and Jason Liartis and Spyridon Kantarelis and Giorgos Stamou. {C}ombining {A}utomatic {A}nnotation with {H}uman {V}alidation for the {S}emantic {E}nrichment of {C}ultural {H}eritage {M}etadata. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 353-368, 2024.

\bibitem{schmidt2024fine} Gleb Schmidt and Veronica Vybornaya and Ivan P. Yamshchikov. {F}ine-{T}uning {P}re-{T}rained {L}anguage {M}odels for {A}uthorship {A}ttribution of the {P}seudo-{D}ionysian {A}rs {R}hetorica. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 369-385, 2024.

\bibitem{schöch2024multilingual} Christof Sch{\"o}ch and Julia Dudar and Evgeniia Fileva and Artjoms {\v S}e{\c l}a. {M}ultilingual {S}tylometry: {T}he influence of language on the performance of authorship attribution using corpora from the {E}uropean {L}iterary {T}ext {C}ollection ({E}LTe{C}). In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 386-408, 2024.

\bibitem{ros2024epistemic} Ruben Ros and Melvin Wevers. {E}pistemic {C}apture through {S}pecialization in {P}ost-{W}orld {W}ar {I}I {P}arliamentary {D}ebate. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 409-426, 2024.

\bibitem{kiessling2024does} Benjamin Kiessling and Thibault Cl{\'e}rice. {D}oes {C}ontext {M}atter ? {E}nhancing {H}andwritten {T}ext {R}ecognition with {M}etadata in {H}istorical {M}anuscripts. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 427-442, 2024.

\bibitem{hagen2024domain} Thora Hagen. {D}omain {A}daptation with {L}inked {E}ncyclopedic {D}ata: {A} Case {S}tudy for {H}istorical {G}erman. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 443-461, 2024.

\bibitem{pannach2024golem} Franziska Pannach and Luotong Cheng and Federico Pianzola. {T}he {G}OL{E}M-{K}nowledge {G}raph and {S}earch {I}nterface: {P}erspectives into {N}arrative and {F}iction. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 462-471, 2024.

\bibitem{kababgi2024recognising} Daniel Kababgi and Giulia Grisot and Federico Pennino and Berenike Herrmann. {R}ecognising non-named spatial entities in literary texts: a novel spatial entities classifier. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 472-481, 2024.

\bibitem{nagy2024bootstrap} Ben Nagy. {B}ootstrap {D}istance {I}mposters: {H}igh precision authorship verification with improved interpretability. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 482-493, 2024.

\bibitem{bamman2024on} David Bamman and Kent K. Chang and Li Lucy and Naitian Zhou. {O}n {C}lassification with {L}arge {L}anguage {M}odels in {C}ultural {A}nalytics. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 494-527, 2024.

\bibitem{mahowald2024integrating} Jamie Mahowald and Benjamin Charles Germain Lee. {I}ntegrating {V}isual and {T}extual {I}nputs for {S}earching {L}arge-{S}cale {M}ap {C}ollections with {C}LI{P}. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 528-547, 2024.

\bibitem{sartini2024deciphering} Bruno Sartini. {D}eciphering {S}till {L}ife {A}rtworks with {L}inked {O}pen {D}ata. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 548-558, 2024.

\bibitem{arnold2024explainable} Taylor Arnold and Lauren Tilton. {E}xplainable {S}earch and {D}iscovery of {V}isual {C}ultural {H}eritage {C}ollections with {M}ultimodal {L}arge {L}anguage {M}odels. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 559-574, 2024.

\bibitem{stewart2024methodology} Spencer Dean Stewart. {A} Methodology for {S}tudying {L}inguistic and {C}ultural {C}hange in {C}hina, 1900-1950. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 575-588, 2024.

\bibitem{wang2024quantitative} Sungpil Wang and Juyong Park. {Q}uantitative {F}ramework for {W}ord-{C}olor {A}ssociation and {A}pplication to 20th {C}entury {A}nglo-{A}merican {P}oetry. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 589-609, 2024.

\bibitem{raffaelli2024promises} Giulio Tani Raffaelli. {P}romises from an {I}nferential {A}pproach in {C}lassical {L}atin {A}uthorship {A}ttribution. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 610-619, 2024.

\bibitem{nusch2024clustering} Carlos Javier Nusch and Gimena Del R{\'\i}o Riande and Leticia Cagnina and Marcelo Luis Errecalde and Leandro Antonelli. {C}lustering {T}asks and {D}ecision {T}rees with {A}ugustan {L}ove {P}oets: {C}ohesion and {S}eparation in {F}eature {I}mportance {E}xtraction. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 620-648, 2024.

\bibitem{heřmánková2024fair} Petra He{\v r}m{\'a}nkov{\'a} and Brian Ballsun-Stanton and Ray Laurence. F{A}IR {T}urn in {E}pigraphy: {L}ow {B}arrier {P}athways to {Q}uantitative and {R}eproducible {R}esearch in {L}atin {E}pigraphy. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 649-661, 2024.

\bibitem{laato2024extracting} Joonatan Laato and Jenna Kanerva and John Loehr and Virpi Lummaa and Filip Ginter. {E}xtracting {S}ocial {C}onnections from {F}innish {K}arelian {R}efugee {I}nterviews {U}sing {L}LMs. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 662-680, 2024.

\bibitem{feldkamp2024sentiment} Pascale Feldkamp and Ea Overgaard Lindhardt and Kristoffer L. Nielbo and Yuri Bizzoni. {S}entiment {B}elow the {S}urface: {O}missive and {E}vocative {S}trategies in {L}iterature and {B}eyond. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 681-706, 2024.

\bibitem{barakat2024computational} Berat Kurar-Barakat and Daria Vasyutinsky-Shapira and Sharva Gogawale and Mohammad Suliman and Nachum Dershowitz. {C}omputational {P}aleography of {M}edieval {H}ebrew {S}cripts. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 707-717, 2024.

\bibitem{jacobsen2024patterns} Mia Jacobsen and Yuri Bizzoni and Pascale Feldkamp Moreira and Kristoffer L. Nielbo. {P}atterns of {Q}uality: {C}omparing {R}eader {R}eception {A}cross {F}anfiction and {C}ommercially {P}ublished {L}iterature. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 718-739, 2024.

\bibitem{boot2024in} Peter Boot and Angel Daza and Carsten Schnober and Willem van Hage. {I}n the {C}ontext of {N}arrative, we {N}ever {P}roperly {D}efined the {C}oncept of {V}alence. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 740-760, 2024.

\bibitem{ziegler2024exploration} Ismail Prada Ziegler. {E}xploration of {E}vent {E}xtraction {T}echniques in {L}ate {M}edieval and {E}arly {M}odern {A}dministrative {R}ecords. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 761-771, 2024.

\bibitem{hansen2024literary} Jens Bjerring-Hansen and Ali Al-Laith and Daniel Hershcovich and Alexander Conroy and Sebastian {\O}rtoft Rasmussen. {L}iterary {T}ime {T}ravel: {D}istinguishing {P}ast and {C}ontemporary {W}orlds in {D}anish and {N}orwegian {F}iction. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 772-787, 2024.

\bibitem{venglarova2024who} Klara Venglarova and Raven Adam and Wiltrud M{\"o}lzer and Saranya Balasubramanian and J{\"o}rn Kleinert and Manfred F{\"u}llsack and Georg Vogeler. {W}ho {A}dvertises in {N}ewspapers? {D}ata {C}riticism in {M}ining {H}istorical {J}ob {A}ds. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 788-801, 2024.

\bibitem{abel2024greatest} Edward Abel and Andrew Goddard. {G}reatest {H}its {V}ersus {D}eep {C}uts: {E}xploring {V}ariety in {S}et-lists {A}cross {A}rtists and {M}usical {G}enres. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 802-828, 2024.

\bibitem{mclachlan2024context} Ross Deans Kristensen-McLachlan and Rebecca M.M. Hicke and M{\'a}rton Kardos and Mette Thun{\o}. {C}ontext is {K}ey({N}MF): {M}odelling {T}opical {I}nformation {D}ynamics in {C}hinese {D}iaspora {M}edia. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 829-847, 2024.

\bibitem{zichert2024tracing} Michael Zichert and Adrian W{\"u}thrich. {T}racing the {D}evelopment of the {V}irtual {P}article {C}oncept {U}sing {S}emantic {C}hange {D}etection. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 848-868, 2024.

\bibitem{sobotkova2024assessing} Adela Sobotkova. {A}ssessing {B}urial {M}ound {I}ntervisibility and {P}rominence at {R}egional {S}cale. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 869-880, 2024.

\bibitem{vandyck2024abbreviation} Caroline Vandyck and Mike Kestemont. {A}bbreviation {A}pplication: {A} Stylochronometric {S}tudy of {A}bbreviations in the {O}euvre of {H}erne\textquotesingle s {S}peculum {S}cribe. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 881-891, 2024.

\bibitem{roald2024visual} Marie Roald and Magnus Breder Birkenes and Lars Gunnars{\o}nn Bag{\o}ien Johnsen. {V}isual {N}avigation of {D}igital {L}ibraries: {R}etrieval and {C}lassification of {I}mages in the {N}ational {L}ibrary of {N}orway\textquotesingle s {D}igitised {B}ook {C}ollection. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 892-905, 2024.

\bibitem{yang2024exploring} Xiaoyan Yang and Federio Pianzola. {E}xploring the {E}volution of {G}ender {P}ower {D}ifference through the {O}megaverse {T}rope on {A}O3 {F}anfiction. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 906-916, 2024.

\bibitem{chang2024subversive} Kent K. Chang and Anna Ho and David Bamman. {S}ubversive {C}haracters and {S}tereotyping {R}eaders: {C}haracterizing {Q}ueer {R}elationalities with {D}ialogue-{B}ased {R}elation {E}xtraction. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 917-937, 2024.

\bibitem{vozhik2024censorship} Ekaterina Vozhik and Kirill Maslinsky and Roman Lisiukov. {C}ensorship as a {D}issociative {F}orce: {A} Case of {S}ovremennik {M}agazine, 1847\textendash 1866. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 938-949, 2024.

\bibitem{langenhorst2024and} Jan Langenhorst and Robert C. Schuppe and Yannick Frommherz. {A}nd then {I} saw it: {T}esting {H}ypotheses on {T}urning {P}oints in a {C}orpus of {U}FO {S}ighting {R}eports. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 950-960, 2024.

\bibitem{zhang2024remember} Xinhao Zhang and Olga Seminck and Pascal Amsili. {R}emember to {F}orget: {A} Study on {V}erbatim {M}emorization of {L}iterature in {L}arge {L}anguage {M}odels. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 961-981, 2024.

\bibitem{kim2024sequencing} Alexander Kim. {S}equencing {L}iterary {R}eception: {T}rajectories of {R}ussian {N}ovels over the {A}fterlife {C}ourse. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 982-998, 2024.

\bibitem{schnober2024page} Carsten Schnober and Renate Smit and Manjusha Kuruppath and Kay Pepping and Leon van Wissen and Lodewijk Petram. {P}age {E}mbeddings: {E}xtracting and {C}lassifying {H}istorical {D}ocuments with {G}eneric {V}ector {R}epresentations. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 999-1011, 2024.

\bibitem{kurzynski2024revolution} Maciej Kurzynski and Aaron Gilkison. {R}evolution + {L}ove: {M}easuring the {E}ntanglements of {S}tate {V}iolence and {E}motions in {E}arly {P}RC. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1012-1022, 2024.

\bibitem{häußler2024animacy} Julian H{\"a}u{\ss}ler and Janis von Keitz and Evelyn Gius. {A}nimacy in {G}erman {F}olktales. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1023-1036, 2024.

\bibitem{bartl2024quantitative} Christoph Bartl and Sharwin Rezagholi and Mareike Schumacher. {A} quantitative study of gender representation and authors\textquotesingle  gender in a large-market print medium. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1037-1052, 2024.

\bibitem{dalfsen2024direct} Arjan van Dalfsen and Folgert Karsdorp and Ayoub Bagheri and Dieuwertje Mentink and Thirza van Engelen and Els Stronks. {D}irect and {I}ndirect {A}nnotation with {G}enerative {A}I: {A} Case {S}tudy into {F}inding {A}nimals and {P}lants in {H}istorical {T}ext. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1053-1074, 2024.

\bibitem{jacomy2024sub} Mathieu Jacomy and Matilde Ficozzi and Anders K. Munk. {S}ub-optimal {R}ecall in {V}isual {C}luster {R}etrieval: {W}hen {C}lusters {L}ook {L}ike {B}ridges. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1075-1085, 2024.

\bibitem{levchenko2024automatic} Maria Levchenko. {A}utomatic {T}ranslation {A}lignment {P}ipeline for {M}ultilingual {D}igital {E}ditions of {L}iterary {W}orks. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1086-1104, 2024.

\bibitem{hicke2024science} Rebecca M. M. Hicke and Ross Deans Kristensen-McLachlan. S{C}IE{N}CE {I}S {E}XP{L}OR{A}TI{O}N: {C}omputational {F}rontiers for {C}onceptual {M}etaphor {T}heory. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1105-1116, 2024.

\bibitem{colliaux2024discourse} David Colliaux and Remi van Trijp. {T}he discourse of the {F}rench method: making old knowledge on market gardening accessible to machines and humans. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1117-1127, 2024.

\bibitem{schlenk2024treating} Martin Schlenk and Thomas Efer and Manuel Burghardt. {T}reating {G}ames as {P}lays? {C}omputational {A}pproaches to the {D}etection of {S}cenes in {G}ame {D}ialogs. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1128-1138, 2024.

\bibitem{ryan2024early} Yann Ryan and Margherita Fantoli. {E}arly {M}odern {B}ook {C}atalogues and {M}ultilingualism: {I}dentifying {M}ultilingual {T}exts and {T}ranslations using {T}itles. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1139-1157, 2024.

\bibitem{illmer2024univariate} Viktor J. Illmer and D{\^\i}lan Canan {\c C}akir and Frank Fischer and Lilly Welz and Carsten Milling. {U}nivariate {S}tatistical {A}nalysis of a {N}on-{C}anonical {L}iterary {G}enre. {Q}uantifying {G}erman-{L}anguage {O}ne-{A}ct {P}lays (1740\textendash 1850). In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1158-1174, 2024.

\bibitem{rebora2024models} Simone Rebora and Gabriele Vezzani. {M}odels of {L}iterary {E}valuation and {W}eb 2.0. {A}n {A}nnotation {E}xperiment with {G}oodreads {R}eviews. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1175-1200, 2024.

\bibitem{walsh2024does} Melanie Walsh and Anna Preus and Elizabeth Gronski. {D}oes {C}hat{G}PT {H}ave a {P}oetic {S}tyle?. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1201-1219, 2024.

\bibitem{schwartz2024text} Haley Anne Schwartz and Paula Jard{\'o}n Giner and Xavier Rubio Campillo. {T}ext {M}ining to unveil {P}rehistoric {P}astness in {M}useums. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1220-1230, 2024.

\bibitem{liew2024computational} Hong Wei Shawn Liew and Miguel Escobar Varela. {C}omputational segmentation of {W}ayang {K}ulit video recordings using a {C}ross-{A}ttention {T}emporal {M}odel. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1231-1241, 2024.

\bibitem{maksimova2024viability} Erika Maksimova and Mari-Anna Meimer and Mari Piirsalu and Priit J{\"a}rv. {V}iability of {Z}ero-shot {C}lassification and {S}earch of {H}istorical {P}hotos. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1242-1258, 2024.

\bibitem{kvinnsland2024rediscovering} Ranveig Kvinnsland and Ingerid L{\o}yning Dale and Lars Magne Tungland. {R}ediscovering the 1890s: {A} Norwegian {P}oetry {C}orpus. In \textit{Proceedings of the Computational Humanities Research Conference}, pp. 1259-1271, 2024.

\bibitem{wu2018budget} Wu, Di and Chen, Xiujun and Yang, Xun and Wang, Hao and Tan, Qing and Zhang, Xiaoxun and Xu, Jian and Gai, Kun. {B}udget constrained bidding by model-free reinforcement learning in display advertising. In \textit{Proceedings of the 27th ACM International Conference on Information and Knowledge Management}, pp. 1443--1451, 2018.

\bibitem{verma2018programmatically} Verma, Abhinav and Murali, Vijayaraghavan and Singh, Rishabh and Kohli, Pushmeet and Chaudhuri, Swarat. {P}rogrammatically interpretable reinforcement learning. In \textit{International conference on machine learning}, pp. 5045--5054. PMLR, 2018.

\bibitem{zhang2024scaling} Zhang, Wei and Li, Dai and Liang, Chen and Zhou, Fang and Zhang, Zhongke and Wang, Xuewei and Li, Ru and Zhou, Yi and Huang, Yaning and Liang, Dong and others. {S}caling {U}ser {M}odeling: {L}arge-scale {O}nline {U}ser {R}epresentations for {A}ds {P}ersonalization in {M}eta. In \textit{Companion Proceedings of the ACM Web Conference 2024}, pp. 47--55, 2024.

\bibitem{zhao2023embedding} Zhao, Xiangyu and Wang, Maolin and Zhao, Xinjian and Li, Jiansheng and Zhou, Shucheng and Yin, Dawei and Li, Qing and Tang, Jiliang and Guo, Ruocheng. {E}mbedding in recommender systems: {A} survey. \textit{arXiv preprint arXiv:2310.18608}, 2023.

\bibitem{koren2009matrix} Koren, Yehuda and Bell, Robert and Volinsky, Chris. {M}atrix factorization techniques for recommender systems. \textit{Computer}, 42, 30--37, 2009. IEEE.

\bibitem{quadrana2018sequence} Quadrana, Massimo and Cremonesi, Paolo and Jannach, Dietmar. {S}equence-aware recommender systems. \textit{ACM computing surveys (CSUR)}, 51, 1--36, 2018. ACM New York, NY, USA.

\bibitem{naumov2019deep} Naumov, Maxim and Mudigere, Dheevatsa and Shi, Hao-Jun Michael and Huang, Jianyu and Sundaraman, Narayanan and Park, Jongsoo and Wang, Xiaodong and Gupta, Udit and Wu, Carole-Jean and Azzolini, Alisson G and others. {D}eep learning recommendation model for personalization and recommendation systems. \textit{arXiv preprint arXiv:1906.00091}, 2019.

\bibitem{liu2022monolith} Liu, Zhuoran and Zou, Leqi and Zou, Xuan and Wang, Caihua and Zhang, Biao and Tang, Da and Zhu, Bolin and Zhu, Yijie and Wu, Peng and Wang, Ke and others. {M}onolith: real time recommendation system with collisionless embedding table. \textit{arXiv preprint arXiv:2209.07663}, 2022.

\bibitem{zhou2019deep} Zhou, Guorui and Mou, Na and Fan, Ying and Pi, Qi and Bian, Weijie and Zhou, Chang and Zhu, Xiaoqiang and Gai, Kun. {D}eep interest evolution network for click-through rate prediction. In \textit{Proceedings of the AAAI conference on artificial intelligence}, pp. 5941--5948, 2019.

\bibitem{gama2014survey} Gama, Jo{\~a}o and {\v Z}liobait{\.e}, Indr{\.e} and Bifet, Albert and Pechenizkiy, Mykola and Bouchachia, Abdelhamid. {A} survey on concept drift adaptation. \textit{ACM computing surveys (CSUR)}, 46, 1--37, 2014. ACM New York, NY, USA.

\bibitem{Zhou2018} Guorui Zhou and Chengru Song and Xiaoqiang Zhu and Ying Fan and  Han Zhu and Xiao Ma and Yanghui Yan and Junqi Jin and Han Li and Kun Gai. {D}eep {I}nterest {N}etwork for {C}lick-{T}hrough {R}ate {P}rediction. In \textit{Proceedings of the 24th ACM SIGKDD International Conference on 
Knowledge Discovery \& Data Mining (KDD \textquotesingle 18)}, pp. 1059--1068, 2018.

\bibitem{cheng2016wide} Cheng, Heng-Tze and Koc, Levent and Harmsen, Jeremiah and Shaked, Tal and Chandra, Tushar and Aradhye, Hrishi and Anderson, Glen and Corrado, Greg and Chai, Wei and Ispir, Mustafa and others. {W}ide \& deep learning for recommender systems. In \textit{Proceedings of the 1st workshop on deep learning for recommender systems}, pp. 7--10, 2016.

\bibitem{covington2016deep} Covington, Paul and Adams, Jay and Sargin, Emre. {D}eep neural networks for youtube recommendations. In \textit{Proceedings of the 10th ACM conference on recommender systems}, pp. 191--198, 2016.

\bibitem{Sutton1998} Sutton, Richard S. and Barto, Andrew G.. {R}einforcement {L}earning: {A}n {I}ntroduction., 2018 . The MIT Press. \url{http://incompleteideas.net/book/the-book-2nd.html}.

\bibitem{grbovic2018real} Grbovic, Mihajlo and Cheng, Haibin. {R}eal-time personalization using embeddings for search ranking at airbnb. In \textit{Proceedings of the 24th ACM SIGKDD international conference on knowledge discovery \& data mining}, pp. 311--320, 2018.

\bibitem{he2017neural} He, Xiangnan and Liao, Lizi and Zhang, Hanwang and Nie, Liqiang and Hu, Xia and Chua, Tat-Seng. {N}eural collaborative filtering. In \textit{Proceedings of the 26th international conference on world wide web}, pp. 173--182, 2017.

\bibitem{mikolov2013distributed} Mikolov, Tomas and Sutskever, Ilya and Chen, Kai and Corrado, Greg S and Dean, Jeff. {D}istributed representations of words and phrases and their compositionality. \textit{Advances in neural information processing systems}, 26, 2013.

\bibitem{barkan2016item2vec} Barkan, Oren and Koenigstein, Noam. {I}tem2vec: neural item embedding for collaborative filtering. In \textit{2016 IEEE 26th international workshop on machine learning for signal processing (MLSP)}, pp. 1--6. IEEE, 2016.

\bibitem{sun2019bert4rec} Sun, Fei and Liu, Jun and Wu, Jian and Pei, Changhua and Lin, Xiao and Ou, Wenwu and Jiang, Peng. B{E}RT4{R}ec: {S}equential recommendation with bidirectional encoder representations from transformer. In \textit{Proceedings of the 28th ACM international conference on information and knowledge management}, pp. 1441--1450, 2019.

\bibitem{koren2008factorization} Koren, Yehuda. {F}actorization meets the neighborhood: a multifaceted collaborative filtering model. In \textit{Proceedings of the 14th ACM SIGKDD international conference on Knowledge discovery and data mining}, pp. 426--434, 2008.

\bibitem{bennett2007netflix} Bennett, James and Lanning, Stan. {T}he netflix prize., 2007. Netflix.

\bibitem{gomez2015netflix} Gomez-Uribe, Carlos A and Hunt, Neil. {T}he netflix recommender system: {A}lgorithms, business value, and innovation. \textit{ACM Transactions on Management Information Systems (TMIS)}, 6, 1--19, 2015. ACM New York, NY, USA.

\bibitem{van2013deep} Van den Oord, Aaron and Dieleman, Sander and Schrauwen, Benjamin. {D}eep content-based music recommendation. \textit{Advances in neural information processing systems}, 26, 2013.

\bibitem{he2014practical} He, Xinran and Pan, Junfeng and Jin, Ou and Xu, Tianbing and Liu, Bo and Xu, Tao and Shi, Yanxin and Atallah, Antoine and Herbrich, Ralf and Bowers, Stuart and others. {P}ractical lessons from predicting clicks on ads at facebook. In \textit{Proceedings of the eighth international workshop on data mining for online advertising}, pp. 1--9, 2014.

\bibitem{mnih2015human} Mnih, Volodymyr and Kavukcuoglu, Koray and Silver, David and Rusu, Andrei A and Veness, Joel and Bellemare, Marc G and Graves, Alex and Riedmiller, Martin and Fidjeland, Andreas K and Ostrovski, Georg and Petersen, Stig and others. {H}uman-level control through deep reinforcement learning. \textit{Nature}, 518, 529--533, 2015. \url{https://doi.org/10.1038/nature14236}.

\bibitem{schulman2015trust} Schulman, John and Levine, Sergey and Abbeel, Pieter and Jordan, Michael and Moritz, Philipp. {T}rust region policy optimization. In \textit{International Conference on Machine Learning (ICML)}, pp. 1889--1897. PMLR, 2015. \url{https://proceedings.mlr.press/v37/schulman15.pdf}.

\bibitem{williams1992simple} Williams, Ronald J.. {S}imple statistical gradient-following algorithms for connectionist reinforcement learning. \textit{Machine Learning}, 8, 229--256, 1992. Springer. \url{https://link.springer.com/article/10.1007/BF00992696}.

\bibitem{cai2023two} Cai, Qingpeng and Xue, Zhenghai and Zhang, Chi and Xue, Wanqi and Liu, Shuchang and Zhan, Ruohan and Wang, Xueliang and Zuo, Tianyou and Xie, Wentao and Zheng, Dong and others. {T}wo-stage constrained actor-critic for short video recommendation. In \textit{Proceedings of the ACM Web Conference 2023}, pp. 865--875, 2023.
\end{thebibliography}